\addcontentsline{toc}{chapter}{Acknowledgments}
\thispagestyle{empty}

\vspace*{10mm}

\begin{center}
{\usekomafont{section} Acknowledgments}
\end{center}

\vspace{5mm}

\begin{center}
Thank you Allah, for all the guidance and support throughout this beautiful journey.
\end{center} 


A special thanks to my adviser, \textit{\textbf{Benedikt Feldotto M.Sc.}}, not only for helping me working on an exciting field but also for his support and motivation. The person who has provided me with all the support and guidance I needed to complete this project and always pushed me with his insights, suggestions, and guidance to make the best out of this thesis. Thank you for everything you have taught me over the past period. I could not have hoped for better supervision.

I am also very grateful to \textit{\textbf{Prof. Dr.-Ing. Alois Christian Knoll}} for accepting me to join the \textit{Human Brain Project} and the opportunity to work on this project and to be part of a great research group and environment.

There are no sufficient words with which to express my gratitude to my lovely family, \textit{\textbf{my mother, father, sisters, brothers and grandparents}} whose endless love and support have shaped my life and whose unwavering faith in me propels me to pursue my dreams. They always encouraged me and believed in me, even in the darkest times. May I always make you proud. Nothing would have ever been possible without you. Thank you for everything.

I would have never been able to finish this work without the support, encouragement, and prayers I received from \textit{\textbf{my family and friends}}.

Finally, I am grateful to be a member of the \textit{Chair of Robotics, Artificial Intelligence, and Real-time Systems} at the Technical University of Munich where I was welcomed, made friends and learned so much during my bachelor. It has been a privilege for me to work in field of reinforcement learning.
